\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-09-06 paper.tex
update

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. We then define the rotation $R$ using a Householder rotation, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  To simplify the notation, in the following we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$.

%\subsection{Reachability constraints using ellipsoidal constraints and their differential}\label{sec:ellipoid constraints}
\rtron{Make sure that, throughout the paper, we use reachability ellipsoid instead of ellipsoidal regions}
We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon. For each one, our goal is to define the function $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}).

@@

>>>>

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. We then define the rotation $R$ using a Householder rotation, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  To simplify the notation, in the following we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
  \begin{align}
    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
  \end{align}
  with $c=\frac{\norm{q_2-q_1}}{2}$.

  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$,$b$ represent the lengths of the major axes.

For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the defined transformation function.

We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon. For each one, our goal is to define the function $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}).

@@

  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
  % \begin{equation}
  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
  % \end{equation}
